### 2024-02-19 documentation/thesis/thesis_document.tex
.

The evaluation of the measurement data showed that the selected sensors
only partially fulfil the defined requirements.

The \emph{TLV493D} and \emph{MMC5603NJ} sensors are both suitable for
characterising permanent magnets and enable linearity compensation with
a defined measurement setup. Although the \emph{MMC5603NJ} has a limited
measuring range, it can still be used for relative comparisons of
permanent magnets without additional devices and without software
calibration. It also has a minimal long-term background noise. Absolute
comparability can be achieved by prior software calibration and using
reference measurements, making it an ideal sensor for the task of
characterising permanent magnets in field tests.

>>>>

The evaluation of the measurement data showed that the selected sensors
only partially fulfil the defined requirements. The \emph{TLV493D} and
\emph{MMC5603NJ} sensors are both suitable for characterising permanent
magnets and enable linearity compensation with a defined measurement
setup. Although the \emph{MMC5603NJ} has a limited measuring range, it
can still be used for relative comparisons of permanent magnets without
additional devices and without software calibration. It also has a
minimal long-term background noise. Absolute comparability can be
achieved by prior software calibration and using reference measurements,
making it an ideal sensor for the task of characterising permanent
magnets in field tests.
